A seamless, client-centric programming model for type safe web applications

### 2014-03-01 paper.tex
Better title
Stress the point that IT'S THE CLIENT, DAMMIT!

\title{Type-safe client-server communication in functional web applications}

@@

>>>>

\title{A seamless, client-centric programming model for type safe web applications}

@@

This is the entry point of our application. Recall that Haste.App applications
are written from the client's perspective, making this the starting point of
the client-side code.
